Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Euler-Lagrange Systems Under Weight and Input Constraints

### 2025-05-02 manuscript.tex
writing... use colored line

\begin{itemize}
    \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
    \item $\mv x=[x_i]_{i\in\{1,\cdots,n\}}\in\R^n$ and $
        \mm A
        := 
        [a_{ij}]
        _{
            i\in\{1,\cdots,n\},j\in\{1,\cdots ,m\}
        }\allowbreak\in\R^{n\times m}
        $ denote a vector and a matrix.
    \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
    \item $\myvec(\mm A):= \left(\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  \right)^\top   $ for $\mm A\in\R^{n\times m}$.
    % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
    % \item $\myvec(A):= [\mycol_1(A)^\top  ,\cdots,\mycol_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
    \item $\lambda_{\min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
    \item $\mm I_n$ denotes the $n\times n$ identity matrix, and $\mm 0_{n\times m}$ denotes the $n\times m$ zero matrix.
\end{itemize}

@@

The main contributions of this study are listed as follows:
\begin{itemize}
    \item A constrained optimization-based neuro-adaptive controller (CONAC) is developed using a DNN, where input constraints and the boundedness of NN weights are formulated as inequality constraints within the adaptation process.
    \item The weight adaptation laws in CONAC are derived using constrained optimization theory to minimize the objective function while satisfying the inequality constraints. The adaptation laws ensure convergence of the weights to the first-order optimality conditions, specifically the Karush-Kuhn-Tucker (KKT) conditions.
    % \item The forward sensitivity method is applied in CONAC to accurately calculate the gradient of the objective function. \MSRY{WILL BE DELETED}
    %, enabling more precise real-time adaptation.
\end{itemize}

@@

The Euler-Lagrange system \eqref{eq:sys1} satisfy some important physical properties \cite[see, Chap. 3 Tab. 3.2.1]{Lewis:1998aa}.
We introduce the following properties:
\begin{prop} 
    The inertia matrix $\rbM$ is symmetric, positive definite and bounded.
    \label{prop:M}
\end{prop}

@@

\begin{figure*}[!t]
    \centering
    \includegraphics[width=.55\linewidth]{src/figures/Controller.drawio.pdf}
    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
    \label{fig:ctrl:diagram}
\end{figure*}

@@

For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i$ for all $i\in \{0,\cdots,k\}$ as 
\begin{equation}
    \wth := 
    \begin{pmatrix}
        \wth_k\\
        \wth_{k-1}\\
        \vdots\\
        \wth_0
    \end{pmatrix}
    =
    \begin{pmatrix}
        \myvec(\wV_k)\\
        \myvec(\wV_{k-1})\\
        \vdots\\
        \myvec(\wV_0)
    \end{pmatrix},
\end{equation}
where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \NN({\q}_n;\wth)$ with respect to $\wth$ is defined as
\begin{equation}
    \pptfrac{\NN}{\wth}=
    \begin{bmatrix}
        \pptfrac{\NN}{\wth_k}&
        \pptfrac{\NN}{\wth_{k-1}}&
    \cdots &
        \pptfrac{\NN}{\wth_0}
    \end{bmatrix}
    \in\R^{n \times \Xi}
    \label{eq. nabla phi}
\end{equation}
where
\begin{equation}
    \pptfrac{\NN}{\wth_i} = 
    \begin{cases}
        (
            \mm I_{l_{k+1}}
            \otimes 
            \act_{k}^\top  
        )
        , 
        &
        i=k
        ,
        \\
        \wV_k^\top\act_{k}' 
        (
            \mm I_{l_{k}}
            \otimes  
            \act_{k-1}^\top  
        )
        , 
        & 
        i=k-1
        ,
        \\
        &
        \vdots 
        \\
        \wV_k^\top\act'_{k} 
        \cdots 
        \wV_1^\top\act_1' 
        (
            \mm I_{l_1}
            \otimes 
            {\q}_n^\top  
        )
        , 
        &
        i = 0
        ,
    \end{cases}
    \label{eq:NN:grad}
\end{equation}
and $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \pptfrac{\act_i}{\NN_{i-1}}$.

@@

% ------------------------------------
% Robot Model Parameters
% -----------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Two-link manipulator parameters of $p\textsuperscript{th}$ link.}
    \centering
    \begin{tabular}{c m{9.5em} c c c }
    % \begin{tabular}{c c c c c}
    \hline
    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline
    \hline 
    $m_p$ & Mass & \multicolumn{2}{c}{2.465 (kg)} \\
    \hline
    $l_p$  & Length & \multicolumn{2}{c}{0.2 (m)} \\  
    \hline
    ${l_c}_p$ & Center of mass & \multicolumn{2}{c}{0.139 (m)} \\
    \hline
    $b_p$   & Viscous friction coef. & \multicolumn{2}{c}{0.1 (Nms)} \\
    \hline
    ${f_c}_p$  & Coulomb friction coef. & \multicolumn{2}{c}{0.24 (Nm)} \\
    \hline
    ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
    \hline
    $I_p$  & Inertia & \multicolumn{2}{c} {0.069 (kgm\textsuperscript{2})} \\
    \hline
    \end{tabular}
    \label{table:system:params}
\end{table}

@@

On the other hand, the existing auxiliary system \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} was used to compare with the proposed CONAC.
The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu,\ \mv{\zeta}\vert_{t=0} = \mv{0}_{2\times1}$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta\in\R_{<0}^{n\times n}$, and $\mm{B}_\zeta\in\R^{n\times n}$.
The auxiliary state $\mv{\zeta}$ is affected by the overflow amount of the control input $\Delta\rbu$, whose entries are defined as $\Delta\tau_{i} = 
\tau_{i}-\max(\underline\tau_i,\min(\overline\tau_i,\tau_i)),\ \forall i\in\{1,2\}$.
The auxiliary state are used in the adaptation law \eqref{eq:adap:th:approx} by substituting $\fe$ with $\fe+\mv{\zeta}$.
Hence, the weights are adapted to reduce not only the tracking error $\fe$ but also the auxiliary state $\mv{\zeta}$, minimizing the control input constraint saturation.

@@

% ------------------------------------
% Controller Parameters
% ------------------------------------
For all controllers ((C$_1$), (C$_2$), (C$_3$), and (C$_4$)), the NN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix. 
The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$, and the same random seed.
Each NN architecture had two hidden layers with four nodes (\ie $k=2$, and $l_0=6, l_1=4, l_2=4$, and $l_3=2$), and the adaptation gain was set to $\alpha=0.5$.
The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,15])$.
The sampling rate of the controller was $250$ Hz considering the real-time implementation.
The weight constraint parameters were selected as $\overline\wth_0=\overline\wth_1=\overline\wth_2=6$. 
The control results were collected via CAN communication with PCAN USB  and recorded in a computer with a sampling rate of $250$ Hz.

@@

% ------------------------------------
% Controller Table
% ------------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Properties of the controllers used in \DHHO{sim? simulation}}
    \label{table:controller}
    \centering
    \begin{tabular}{c l l}
    \hline
        \!&\!\bf{Description}\!&\!\bf{Input Constraint}\!\\
    \hline
    \hline
        (C$_1$)\!&\!large $\beta_j$\!&\!$\overline{\tau}=11,\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
    \hline
        (C$_2$)\!&\!small $\beta_j$\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau_2}=2.5$ \\
    \hline
        (C$_3$)\!&\!no $\rbu$ constraints\!&\!$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$ \\
    \hline
        (C$_4$)\!&\!aux. sys.\!&\!$\overline{\tau}_1\!=\!-\underline{\tau}_1\!=\!9.682,\overline{\tau_2}\!=\!-\underline{\tau_2}\!=\!2.5$\!\\
    \hline
    \end{tabular}
    \label{table:controllers}
\end{table}

\begin{figure*}[t]
  \centering
    \subfloat[Tracking result of $q_1$.]{
    %   \includegraphics
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % fig/Fig1.pdf
        src/measurement/figures/compare/Fig1.eps
      }%
      \label{fig:ctrl:result:q1}}
    \hfill
    \subfloat[Tracking result of $q_2$.]{
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % src/measurement/figures/compare/Fig11.eps
        src/measurement/figures/compare/Fig2.eps
      }%
      \label{fig:ctrl:result:q2}}
    \vfill
      \subfloat[Control input $\tau_1$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/measurement/figures/compare/Fig3.eps
        }%
        \label{fig:ctrl:result:tau:1}}
    \hfill
      \subfloat[Control input $\tau_2$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/measurement/figures/compare/Fig4.eps
        }%
        \label{fig:ctrl:result:tau:2}}
        \vfill
    \subfloat[Norm of control input $\rbu$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/measurement/figures/compare/Fig5.eps
        }%
        \label{fig:ctrl:result:tau:norm}}
    \hfill
    \subfloat[Norm of weights ${\estwth}_i$.]{
        % \includegraphics
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            % fig/Fig7.pdf
            src/measurement/figures/compare/Fig7.eps
        }%
        \label{fig:ctrl:result:weight}}        
    \caption{
  \DHHO{sim?: Simulation} results of (C$_1$) (blue), (C$_2$) (cyan), (C$_3$) (gray), and reference signal of $\qd$ (red dashed line).
  }
\label{fig:ctrl:result}
\end{figure*}

\begin{figure}[t]
    \centering
    \subfloat[Control input $\tau$ in time interval from $19$ s to $21$ s (bird's eye view).]{
    % \subfloat[Auxiliary states $\mv{\zeta}$ of CONAC-AUX.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/compare/Fig6.eps
        }%
        \label{fig:ctrl:result:scope:control}}
        \vfill
    \subfloat[Lagrange multipliers $\lambda_j$  in time interval from $19$ s to $21$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/compare/Fig8.eps
        }%
        \label{fig:ctrl:result:scope:beta}}
        \vfill
    \subfloat[Auxiliary states in time interval from $19$ s to $21$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/compare/Fig9.eps
        }%
        \label{fig:ctrl:result:scope:aux}}
  \caption{
    Constraint handling process of (C$_1$) (blue), (C$_2$) (cyan), and (C$_3$) (gray) in time interval from $19$ s to $21$ s.
  }
\label{fig:ctrl:result:scope}
\end{figure}

@@

The simulation results are shown in Fig.~\ref{fig:ctrl:result} and the quantitative comparison of the tracking performance is given in Table~\ref{tab:sim:L2}.
Across the two episodes, all controllers enhanced their tracking performances about $70 \%$ for (C$_1$), $63.1 \%$ for (C$_2$), $63.7 \%$ for (C$_3$), and $18.5 \%$ for (C$_4$) in $L_2$ norm of $e_1$, and $88.4 \%$ for (C$_1$), $76.9 \%$ for (C$_2$), $72.8 \%$ for (C$_3$), and $67.1 \%$ for (C$_4$) in $L_2$ norm of $e_2$, respectively, as shown in Table~\ref{tab:sim:L2}.
Qualitatively, as described in Fig.~\ref{fig:ctrl:result:q1} and Fig.~\ref{fig:ctrl:result:q2}, the oscillations were suppressed in the second episode, as well.
This results lead to the conclusion that the NNs in all controllers were able to learn the ideal control input $\rbu^*$ properly, by the filtered error $\fe$, despite the fact that $\rbu^*$ was not known in advance.
Moreover, since the learning began from the random initialization of the weights and no prior knowledge of the system, the online learning capability of the proposed CONAC was demonstrated.

In addition, it is notable that in both episodes, all controllers failed to track the desired trajectory of $q_1$ in time interval from $7.5$ s to $8.5$ for Episode $1$, and from $19.5$ s to $20.5$ s for Episode $2$.
This is because the control inputs were saturated in the time intervals, as shown in Fig.~\ref{fig:ctrl:result:tau:1} and Fig.~\ref{fig:ctrl:result:tau:norm}.
However,

The tracking performance of CONAC, (\ie (C$_1$), and (C$_3$)), outperformed (C$_2$) in both episodes, as shown in Table~\ref{tab:sim:L2}.
This is because, (as wil be discussed in Section \ref{sec:sim:constraint}) (C$_1$) was able to use the full capability of the actuator, while (C$_2$) was limited its first link actuator due to the feature of the auxiliary system.

% ------------------------------------
% Control Input Saturation
% ------------------------------------
\subsubsection{Constraint Handling} \label{sec:sim:constraint}

In this section, the constraint handling capability of all controllers are investigated.
First, the weight norm constraints $c_{\theta_i},\ \forall i\in\{0,1,2\}$ were not violated, as shown in Fig.~\ref{fig:ctrl:result:weight}, since the limits $\overline{\theta}_i,\ \forall i\in\{0,1,2\}$ were set sufficiently large.

As shown in Fig.~\ref{fig:ctrl:result:tau:1}, Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, all controllers satisfied the control input saturation illustrated in Fig.~\ref{fig:robot:sat}, with $c_{\rbu},c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ for (C$_1$) and (C$_3$), and $c_{\overline\tau_1},c_{\underline\tau_1},c_{\overline\tau_2}$, and $c_{\underline\tau_2}$ for (C$_2$), as the weights were adapted to reduce the constraint violations, using Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal{I}$, and auxiliary state $\mv{\zeta}$, respectively.
It is worth to note that the control input constraints were violated repeatedly, since the controllers were implemented in discrete time with a low sampling rate of $250$ Hz.

@@

Even though all controllers satisfied the input saturation, (C$_2$) was not able to use the full capability of the actuator, as shown in Fig.~\ref{fig:ctrl:result:scope:control} which shows the bird-eye view of the control input $\rbu$ in time interval from $19$ s to $21$ s.
This is because, as aforementioned, the auxiliary system only considers the input bound constraint, and the control input bound constraint for first link was imposed to approximately match the maximum allowable norm of the control input $\overline\tau$, instead of $c_{\rbu}$.
In contrast, (C$_1$) and (C$_3$) were able to use the full capability of the actuator with the combination of the input bound constraints $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$, and the nonlinear input norm constraint $c_{\rbu}$ which is completely match the feasible domain of the control input $\Theta_{\mysat}$.

@@

\DHHO{sim? : Simulation results} validated the superior performance of CONAC compared to conventional methods, such as DNN-BSC and DNN-BSC-A. CONAC not only handled complex input constraints but also managed the weight norm constraints rigorously, leading to improved tracking accuracy and stability without notable oscillations.

>>>>

\begin{itemize}
    \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
    \item A vector and matrix are denoted by $\mv{x}=[x_i]_{i\in\{1,\cdots,n\}}\in\R^n$ and $
        \mm A
        := 
        [a_{ij}]
        _{
            i\in\{1,\cdots,n\},j\in\{1,\cdots ,m\}
        }\allowbreak\in\R^{n\times m}
        $, respectively.
    \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
    \item $\myvec(\mm A):=(\myrow_1(\mm A^\top),\cdots,\myrow_m(\mm A^\top)  )^\top$ for $\mm{A}\in\R^{n\times m}$, denotes vectorization of $\mm A$.
    % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
    % \item $\myvec(A):= [\mycol_1(A)^\top  ,\cdots,\mycol_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
    \item $\lambda_{\min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
    \item $\mm I_n$ denotes the $n\times n$ identity matrix, and $\mm 0_{n\times m}$ denotes the $n\times m$ zero matrix.
\end{itemize}

@@

The main contributions of this study are listed as follows:
\begin{itemize}
    \item A constrained optimization-based neuro-adaptive controller (CONAC) is developed using a DNN, where input constraints and the boundedness of NN weights are formulated as inequality constraints within the adaptation process.
    \item The weight adaptation laws in CONAC are derived using constrained optimization theory to minimize the objective function while satisfying the inequality constraints. The adaptation laws ensure convergence of the weights to the first-order optimality conditions, specifically the Karush-Kuhn-Tucker (KKT) conditions defined in \cite[Chap. 12 Thm. 12.1]{Nocedal:2006aa}. 
    % \item The forward sensitivity method is applied in CONAC to accurately calculate the gradient of the objective function. \MSRY{WILL BE DELETED}
    %, enabling more precise real-time adaptation.
\end{itemize}

@@

The Euler-Lagrange system \eqref{eq:sys1} satisfy some important physical properties \cite[see,][Chap. 3 Tab. 3.2.1]{Lewis:1998aa}.
We introduce the following properties:
\begin{prop} 
    The inertia matrix $\rbM$ is symmetric, positive definite and bounded.
    \label{prop:M}
\end{prop}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=.99\linewidth]{src/figures/Controller.drawio.pdf}
    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
    \label{fig:ctrl:diagram}
\end{figure}

@@

For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i$ for all $i\in \{0,\cdots,k\}$ as 
\begin{equation}
    \wth := 
    \begin{pmatrix}
        \wth_k\\
        \wth_{k-1}\\
        \vdots\\
        \wth_0
    \end{pmatrix}
    =
    \begin{pmatrix}
        \myvec(\wV_k)\\
        \myvec(\wV_{k-1})\\
        \vdots\\
        \myvec(\wV_0)
    \end{pmatrix},
\end{equation}
where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \NN({\q}_n;\wth)$ with respect to $\wth$ is defined as
\begin{equation}
    \pptfrac{\NN}{\wth}=
    \begin{bmatrix}
        \pptfrac{\NN}{\wth_k}&
        \pptfrac{\NN}{\wth_{k-1}}&
    \cdots &
        \pptfrac{\NN}{\wth_0}
    \end{bmatrix}
    \in\R^{n \times \Xi}
    \label{eq:gradient:phi}
\end{equation}
where
\begin{equation}
    \pptfrac{\NN}{\wth_i} = 
    \begin{cases}
        (
            \mm I_{l_{k+1}}
            \otimes 
            \act_{k}^\top  
        )
        , 
        &
        i=k
        ,
        \\
        \wV_k^\top\act_{k}' 
        (
            \mm I_{l_{k}}
            \otimes  
            \act_{k-1}^\top  
        )
        , 
        & 
        i=k-1
        ,
        \\
        &
        \vdots 
        \\
        \wV_k^\top\act'_{k} 
        \cdots 
        \wV_1^\top\act_1' 
        (
            \mm I_{l_1}
            \otimes 
            {\q}_n^\top  
        )
        , 
        &
        i = 0
        ,
    \end{cases}
    \label{eq:NN:grad}
\end{equation}
and $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \pptfrac{\act_i}{\NN_{i-1}}$.

@@

% ------------------------------------
% Robot Model Parameters
% -----------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Two-link manipulator parameters of $p\textsuperscript{th}$ link.}
    \centering
    \begin{tabular}{c m{9.5em} c c c }
    % \begin{tabular}{c c c c c}
    \hline
    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline
    \hline 
    $m_p$ & Mass & \multicolumn{2}{c}{2.465 (kg)} \\
    \hline
    $l_p$  & Length & \multicolumn{2}{c}{0.2 (m)} \\  
    \hline
    ${l_c}_p$ & Center of mass & \multicolumn{2}{c}{0.139 (m)} \\
    \hline
    % $b_p$   & Viscous friction coef. & \multicolumn{2}{c}{0.1 (Nms)} \\
    % \hline
    % ${f_c}_p$  & Coulomb friction coef. & \multicolumn{2}{c}{0.24 (Nm)} \\
    % \hline
    % ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
    % \hline
    $I_p$  & Inertia & \multicolumn{2}{c} {0.069 (kgm\textsuperscript{2})} \\
    \hline
    \end{tabular}
    \label{table:system:params}
\end{table}

@@

On the other hand, the existing auxiliary system \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} was used to compare with the proposed CONAC.
The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu,\ \mv{\zeta}\vert_{t=0} = \mv{0}_{2\times1}$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta\in\R_{<0}^{n\times n}$, and $\mm{B}_\zeta\in\R^{n\times n}$.
The auxiliary state $\mv{\zeta}$ is affected by the overflow amount of the control input $\Delta\rbu$, whose entries are defined as $\Delta\tau_{i} = 
\tau_{i}-\max(\underline\tau_i,\min(\overline\tau_i,\tau_i)),\ \forall i\in\{1,2\}$.
The auxiliary state are used in the adaptation law \eqref{eq:adap:th:approx} by substituting $\fe$ with $\fe+\mv{\zeta}$.
Consequently, the weights are adapted to reduce not only the tracking error $\fe$ but also the auxiliary state $\mv{\zeta}$, minimizing the control input constraint saturation.

@@

% ------------------------------------
% Controller Parameters
% ------------------------------------
For all controllers ((C$_1$), (C$_2$), (C$_3$), and (C$_4$)), the NN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix. 
The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$, and the same random seed.
Each NN architecture had two hidden layers with four nodes (\ie $k=2$, and $l_0=6, l_1=4, l_2=4$, and $l_3=2$), and the adaptation gain was set to $\alpha=0.5$.
The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,15])$.
The sampling rate of the controller was $250$ Hz considering the real-time implementation.
The weight constraint parameters were selected as $\overline\wth_0=\overline\wth_1=\overline\wth_2=6$.
\MSRY{어차피 내부는 안걸리니까 그림 더 깔끔하게 다 6이라고 함} 
The control results were collected via CAN communication with PCAN USB  and recorded in a computer with a sampling rate of $250$ Hz.

@@

% ------------------------------------
% Controller Table
% ------------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Properties of the controllers}
    \label{table:controller}
    \centering
    \begin{tabular}{c l l}
    \hline
        \!&\!\bf{Description}\!&\!\bf{Input Constraint}\!\\
    \hline
    \hline
        (C$_1$)\!&\!large $\beta_j$\!&\!$\overline{\tau}=11,\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
    \hline
        (C$_2$)\!&\!small $\beta_j$\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau_2}=2.5$ \\
    \hline
        (C$_3$)\!&\!no $\rbu$ constraints\!&\!$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$ \\
    \hline
        (C$_4$)\!&\!aux. sys.\!&\!$\overline{\tau}_1\!=\!-\underline{\tau}_1\!=\!9.682,\overline{\tau_2}\!=\!-\underline{\tau_2}\!=\!2.5$\!\\
    \hline
    \end{tabular}
    \label{table:controllers}
\end{table}

\begin{figure*}[t]
  \centering
    \subfloat[Tracking result of $q_1$.]{
    %   \includegraphics
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % fig/Fig1.pdf
        src/measurement/figures/compare/Fig1.eps
      }%
      \label{fig:ctrl:result:q1}}
    \hfill
    \subfloat[Tracking result of $q_2$.]{
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % src/measurement/figures/compare/Fig11.eps
        src/measurement/figures/compare/Fig2.eps
      }%
      \label{fig:ctrl:result:q2}}
    \vfill
      \subfloat[Control input $\tau_1$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/measurement/figures/compare/Fig3.eps
        }%
        \label{fig:ctrl:result:tau:1}}
    \hfill
      \subfloat[Control input $\tau_2$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/measurement/figures/compare/Fig4.eps
        }%
        \label{fig:ctrl:result:tau:2}}
        \vfill
    \subfloat[Norm of control input $\rbu$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/measurement/figures/compare/Fig5.eps
        }%
        \label{fig:ctrl:result:tau:norm}}
    \hfill
    \subfloat[Norm of weights ${\estwth}_i$.]{
        % \includegraphics
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            % fig/Fig7.pdf
            src/measurement/figures/compare/Fig7.eps
        }%
        \label{fig:ctrl:result:weight}}        
    \caption{
    Real-time implementation results of (C$_1$) \protect\colorLine{blue}{solid}, (C$_2$) \protect\colorLine{cyan}{solid}, (C$_3$) \protect\colorLine{gray}{solid}, (C$_4$) \protect\colorLine{magenta}{solid}, and reference signal $\qd$ \protect\colorLine{red}{dashed}. 
  }
\label{fig:ctrl:result}
\end{figure*}

\begin{figure}[t]
    \centering
    \subfloat[Control input $\tau$ in time interval from $29.4$ s to $31.9$ s (bird's eye view).]{
    % \subfloat[Auxiliary states $\mv{\zeta}$ of CONAC-AUX.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/compare/Fig6.eps
        }%
        \label{fig:ctrl:result:scope:control}}
        \vfill
    \subfloat[Lagrange multipliers $\lambda_j$  in time interval from $29.4$ s to $31.9$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/compare/Fig8.eps
        }%
        \label{fig:ctrl:result:scope:beta}}
        \vfill
    \subfloat[Auxiliary states in time interval from $29.4$ s to $31.9$ s.]{
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/compare/Fig9.eps
        }%
        \label{fig:ctrl:result:scope:aux}}
  \caption{
    Constraint handling process of (C$_1$) \protect\colorLine{blue}{solid}, (C$_2$) \protect\colorLine{cyan}{solid}, (C$_3$) \protect\colorLine{gray}{solid}, (C$_4$) \protect\colorLine{magenta}{solid} in time interval from $29.4$ s to $31.9$ s.
  }
\label{fig:ctrl:result:scope}
\end{figure}

@@

The real-time implementation results are shown in Fig.~\ref{fig:ctrl:result} and the quantitative comparison of the tracking performance is given in Table~\ref{tab:sim:L2}.
Across the two episodes, all controllers enhanced their tracking performances about $70 \%$ for (C$_1$), $63.1 \%$ for (C$_2$), $63.7 \%$ for (C$_3$), and $18.5 \%$ for (C$_4$) in $L_2$ norm of $e_1$, and $88.4 \%$ for (C$_1$), $76.9 \%$ for (C$_2$), $72.8 \%$ for (C$_3$), and $67.1 \%$ for (C$_4$) in $L_2$ norm of $e_2$, respectively, as shown in Table~\ref{tab:sim:L2}.
Qualitatively, as described in Fig.~\ref{fig:ctrl:result:q1} and Fig.~\ref{fig:ctrl:result:q2}, the oscillations were suppressed in the second episode.
This results lead to the conclusion that the NNs in all controllers were able to learn the ideal control input $\rbu^*$ properly, by the filtered error $\fe$, despite the fact that $\rbu^*$ was not known in advance.
Moreover, since the learning began from the random initialization of the weights and no prior knowledge of the system, the online learning capability of the proposed CONAC was demonstrated.

In addition, it is notable that in both episodes, all controllers failed to track the desired trajectory of $q_1$ in time interval from $17.5$ s to $19.9$ for Episode $1$, and from $29.5$ s to $31.9$ s for Episode $2$.
This is because the control inputs were saturated in the time intervals, as shown in Fig.~\ref{fig:ctrl:result:tau:1} and Fig.~\ref{fig:ctrl:result:tau:norm}.

The tracking performances of CONAC with control input constraints, (\ie (C$_1$), and (C$_2$)), outperformed CONAC with the auxiliary system (C$_4$) in both episodes, as shown in Table~\ref{tab:sim:L2}.
This is because, (as wil be discussed in Section \ref{sec:sim:constraint}) (C$_1$), and (C$_2$) were able to use the full capability of the actuator, while (C$_4$) was limited its first link actuator due to the feature of the auxiliary system.
The tracking performance of (C$_3$) was also better than (C$_4$), but worse than (C$_1$) and (C$_2$), since the control input constraints were not considered in (C$_3$).

% ------------------------------------
% Control Input Saturation
% ------------------------------------
\hfill
\subsubsection{Constraint Handling} \label{sec:sim:constraint}

In this section, the constraint handling capability of all controllers are investigated.

@@

As shown in Fig.~\ref{fig:ctrl:result:tau:1}, Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, all controllers except (C$_3$) which did not consider the control input saturation, satisfied the control input saturation illustrated in Fig.~\ref{fig:robot:sat}, with $c_{\rbu},c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ for (C$_1$), and (C$_2$), and $c_{\overline\tau_1},c_{\underline\tau_1},c_{\overline\tau_2}$, and $c_{\underline\tau_2}$ for (C$_4$), as the weights were adapted to reduce the constraint violations, using Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal{I}$, and auxiliary state $\mv{\zeta}$, respectively.
It is worth to note that the control input constraints were violated repeatedly, since the controllers were implemented in discrete time with a low sampling rate of $250$ Hz.

@@

A real-time implementation validated the superior performance of CONAC compared to conventional methods, such as DNN-BSC and DNN-BSC-A. CONAC not only handled complex input constraints but also managed the weight norm constraints rigorously, leading to improved tracking accuracy and stability without notable oscillations.
